%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Chan Zuckerberg Biohub}{499 Illinois St\\San Francisco, CA 94115}
\date{\today}
\opening{Dear Chan Zuckerberg Biohub Evaluation Team,}
\closing{Warmest,}
% \enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

% This cover letter follows the "Me, you, us together, and request for response" template

[Me] Hope the holidays are treating you well. This is Olga Botvinnik, a  Bioinformatics and Systems Biology PhD candidate in Dr. Gene Yeo’s lab at UCSD. In my PhD, I’ve focused on single-cell transcriptomics, especially applied to neural development and alternative splicing. I’ve written several open-source Python packages, including \href{https://github.com/YeoLab/outrigger}{detecting and quantifying de novo alternative splicing events}, \href{https://github.com/YeoLab/anchor}{classifying exons as bimodal}, \href{https://github.com/YeoLab/bonvoyage}{visualizing changes in splicing between populations}, and tying it all together with \href{https://github.com/YeoLab/flotilla/}{integrative, reproducible machine learning analysis for large-scale datasets}. I’ve used these softwares together in my paper (\href{https://drive.google.com/file/d/0B44mjlWGbPILeUJVdWMtb0xDWDg/view?usp=sharing}{link}) that is currently in review at Molecular Cell.

[You] The Chan-Zuckerburg Institute’s vision of curing all diseases is a bold, adautious goal that will change
the course of humanity. By deeply investing in basic science research, the babbling brook of the
knowledge behind disease cures will become a tsunami to reckon with. The Human Cell Atlas alone
will push healthcare towards molecular medicine, allowing for patients and doctors to regularly
monitor cellular states, and respond quickly if something goes awry. The scale of the Human Cell
Atlas is monstrous, impossible, exactly what doubters said about the Human Genome Project, and I
want to be there to prove them wrong.

[Us together] By working on the Human Cell Atlas, I will leverage my expertise in using single-cell alternative
splicing to tease apart subtle signals within cellular populations. I would like to continue working on
the critical biological question of "What \emph{is| a cell type?" and developing open-source tools for machine
learning in biology. I believe in the near future, there will be consumer sequencing machines and I
want to be part of the future that builds the foundation for widespread adoption of molecular
medicine, where citizens are scientists, too.

[Closing and polite request for response] Do you think this sounds like a good fit? My dissertation committee is on board with a May graduation date so I’m looking to start in the summer. I’ve attached my CV for reference. I look forward to hearing from you soon.


\makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\clearpage
